Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-27 latex/comp_or.tex
Paper Comp OR update

According to \citet[p.271]{Breshears2009}, a {\it Process} is the operating system’s spawned and controlled entity that encapsulates an executing application. A process has two main jobs: the first is to hold the application's resources, and the second is to carry out the application's instructions.

@@

We ran Algorithm \ref{alg:main} in the 6 scenarios described in Table \ref{tab:scenarios}, considering 3 methods for node-by-node resolution: the {\it Gurobi} MIP solver, {\it Shims}, and {\it mpShims} (Algorithm \ref{alg:mpShims}).

@@

The average tour values were presented for $f$ and, for the run time, the worst result obtained. To facilitate the comparison between the methods, we added a last column in these tables, where two values are indicated:
\begin{itemize}
	\item {\bf Normalized}: value between 0 and 1, which corresponds to the ratio between the sum of $f$\/ values obtained by the method in all scenarios and the sum of the best values obtained among all methods in all scenarios. The higher the value of {\bf Normalized}, the closer the method approached the best solutions found.
	\item {\bf Speedup}: ratio of the sums of the worst runtimes of all scenarios and the sum of the method runtimes in all scenarios. The method with the highest {\bf Speed-up}\/ is the fastest.
\end{itemize}

@@

\begin{table}[H]
	\centering
	\caption{Volume surpluses, methods and scenarios results}  \label{tab:results}
	\footnotesize
	%\scriptsize
	\begin{tabular}{crcccccccc}
		\toprule
		{\bf Volume}     &  {\bf Resolution}   &                              &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\it surplus}    & {\it method}        & {\bf Results}                &{\bf 1}    &{\bf 2}    &{\bf 3}    &{\bf 4}    &{\bf 5}    &{\bf 6}    &{\bf Speedup} \\
		\toprule

@@

		\multirow{6}{*}{$1.2$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 12.23}&{\it 8.67} &{\it 12.67}&{\it 15.36}&{\it 16.29}&{\it 16.20}&  \specialcell{{\bf 1.00}\\-} \\%  8142

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &     10.34 &     8.50  &     12.42 &     15.06 &     15.97 &     15.88 &  0.96 \\% 7817
		&                                                & {\it run time (s)} &     < 1   &     3     &     5     &     20    &     58    &     352   &  1.00 \\% 439			
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &   12.96   &   7.53    &  12.28    &   13.20   &  13.71    &   13.44   &  0.90\\% 7278
		&                                                & {\it run time (s)} &     < 1   &     2     &     2     &     8    &     22    &     120   &  {\bf 2.80}\\%

@@

		\multirow{6}{*}{$1.5$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 17.01}&{\it 12.45}&{\it 18.02}&{\it 22.03}&{\it 23.09}&{\it 22.35}&  \specialcell{{\bf 1.00}\\-} \\%11495

@@

		\midrule
		\multirow{6}{*}{$2.0$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 24.56}&{\it 17.47}&{\it 25.19}&{\it 27.94}&{\it 29.90}&{\it 27.60 }&  \specialcell{{\bf 1.00}\\-} \\%15266

@@

@@

We solved all scenarios and instances with {\it Gurobi} in a relaxed linear model, {\it Relaxed Gurobi}. This is good for the reader to have an idea of the real performance differences between serial and parallel {\it Shims}.

{\it Shims} had a quality performance very close to the {\it Relaxed Gurobi} upper bound solution, and, as to the {\bf Speedup}, on average, {\it mpShims} was 2 times faster than {\it Shims}. Theoretically, it could be more, but due to the burden of sharing, for reading and writing, the CG deviation and the list of items among the processes (pallets), the {\it race condition} management limited {\it mpShims} performance.

@@

\vspace{2.0mm}
\begin{table}[!ht]
\centering
\caption{Parallel 3D packing time increment}  \label{tab:3d}
\scriptsize
\begin{tabular}{c S[table-format=-1.1] S[table-format=-1.1] S[table-format=-1.1]}
\toprule
&   \multicolumn{3}{c}{\bf Average tour time - 3D packing}  \\
\cmidrule{2-4}
& {\bf without} & {\bf with} & {\bf increment} \\
{\bf Scenario} & {\bf (s)}    & {\bf (s)}   & {\bf (times)} \\		
\midrule
$1$ &   1 &   15 & 15 \\
$2$ &   5 &   76 & 15 \\
$3$ &   8 &   97 & 12 \\
$4$ &  35 &  330 &  9 \\ 
$5$ &  98 &  740 &  8 \\    
$6$ & 591 & 3709 &  6 \\                                                                  
\bottomrule
\end{tabular}
\end{table}

@@

\vspace{2.0mm}
\begin{table}[!ht]
\centering
\caption{Average distances minimization}  \label{tab:ground}
%\footnotesize
\scriptsize
\begin{tabular}{c S[table-format=-1.1] S[table-format=-1.1] S[table-format=-1.3]}
\toprule
& {\bf Before} & {\bf After} & {\bf Improvement} \\
{\bf Scenario} & {\bf (m)}    & {\bf (m)}   & {\bf (\%)} \\		
\midrule
$1$ &  32.7 & 28.7 & -12.3 \\
$2$ & 193.3 & 188.9 & -2.3 \\
$3$ & 152.0 & 152.0 &  0.0 \\
$4$ & 134.0 & 130.7 & -2.4 \\ 
$5$ & 118.0 & 116.1 & -1.6 \\    
$6$ & 105.2 & 104.8 & -0.4 \\                                                                  
\bottomrule
\end{tabular}
\end{table}

>>>>

According to \cite[p.271]{Breshears2009}, a {\it Process} is the operating system’s spawned and controlled entity that encapsulates an executing application. A process has two main jobs: the first is to hold the application's resources, and the second is to carry out the application's instructions.

@@

We ran Algorithm \ref{alg:main} in the 6 scenarios described in Table \ref{tab:scenarios}, considering 3 methods for node-by-node resolution: the state-of-the-art {\it Gurobi} MIP solver, {\it Shims}, and {\it mpShims} (Algorithm \ref{alg:mpShims}).

@@

The average tour values were presented for $f$ and, for the run time, the worst result obtained. To facilitate the comparison between the methods, we added a last column in these tables, where two values are indicated:
\begin{itemize}
	\item {\bf Normalized}: value between 0 and 1, which corresponds to the ratio between the sum of $f$\/ values obtained by the method in all scenarios and the sum of the best values obtained among all methods in all scenarios. The higher the value of {\bf Normalized}, the closer the method approached the best solutions found.
	\item {\bf Speedup}: ratio of the sums of the worst run times of all scenarios and the sum of the method run times in all scenarios. The method with the highest {\bf Speed-up}\/ is the fastest.
\end{itemize}

@@

\begin{table}[H]
	\centering
	\caption{Volume surpluses, methods and scenarios results {\bf before} 3D packing}  \label{tab:results}
	\footnotesize
	%\scriptsize
	\begin{tabular}{crcccccccc}
		\toprule
		{\bf Volume}     &  {\bf Resolution}   &                              &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\it surplus}    & {\it method}        & {\bf Results}                &{\bf 1}    &{\bf 2}    &{\bf 3}    &{\bf 4}    &{\bf 5}    &{\bf 6}    &{\bf Speedup} \\
		\toprule

@@

		\multirow{6}{*}{$1.2$}&$Relaxed$                 & $f$         &{\it 12.23}&{\it 8.67} &{\it 12.67}&{\it 15.36}&{\it 16.29}&{\it 16.20}&  \specialcell{{\bf 1.00}\\-} \\%  8142
		&                      $MIP$                     & {\it run time (s)} &     3     &     13    &     20    &     78   &      198  &     1103  &  1.00 \\% 439							
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &     10.34 &     8.50  &     12.42 &     15.06 &     15.97 &     15.88 &  0.96 \\% 7817
		&                                                & {\it run time (s)} &     < 1   &     3     &     5     &     20    &     58    &     352   &  1.00 \\% 439			
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &   12.96   &   7.53    &  12.28    &   13.20   &  13.71    &   13.44   &  0.90\\% 7278
		&                                                & {\it run time (s)} &     < 1   &     2     &     2     &     8    &     22    &     120   &  {\bf 2.80}\\%

@@

		\multirow{6}{*}{$1.5$}&\specialcell{$Relaxed$\\$MIP solver$}& $f$         &{\it 17.01}&{\it 12.45}&{\it 18.02}&{\it 22.03}&{\it 23.09}&{\it 22.35}&  \specialcell{{\bf 1.00}\\-} \\%11495

@@

		\midrule
		\multirow{6}{*}{$2.0$}&\specialcell{$Relaxed$\\$MIP solver$}& $f$         &{\it 24.56}&{\it 17.47}&{\it 25.19}&{\it 27.94}&{\it 29.90}&{\it 27.60 }&  \specialcell{{\bf 1.00}\\-} \\%15266

@@

Table \ref{tab:results2} presents the results of the MIP solver compared to {\it Shims} and {\it mpShims}, after the post-optimization with the multiprocessing 3D packing.

\begin{table}[H]
	\centering
	\caption{Volume surpluses, methods and scenarios results {\bf after} 3D packing}  \label{tab:results2}
	\footnotesize

\color{blue}{

	%\scriptsize
	\begin{tabular}{crcccccccc}
		\toprule
		{\bf Volume}     &  {\bf Resolution}   &                              &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\it surplus}    & {\it method}        & {\bf Results}                &{\bf 1}    &{\bf 2}    &{\bf 3}    &{\bf 4}    &{\bf 5}    &{\bf 6}    &{\bf Speedup} \\
		\toprule

		\multirow{6}{*}{$1.2$}&\specialcell{$Relaxed$\\$MIP solver$}& $f$            &{\it 11.47}&{\it 7.24} &{\it 10.78}&{\it 12.06}&{\it 12.97}&{\it 12.44}&  \specialcell{{\bf 1.00}\\-} \\%  8142
		&                                                & {\it run time (s)} &     6     &     25    &     41    &     158   &      401  &     2161  &  1.00 \\% 439					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &    9.05   &   5.11    &   9.75    &   10.96   &   12.86   &   13.25   &  0.96 \\% 7817
		&                                                & {\it run time (s)} &     16    &     68    &     94    &    323    &    719    &    3549   &  1.00 \\% 439			
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &    12.14  &   7.29    &   10.36   &   12.63   &   14.04   &   13.92   &  0.90\\% 7278
		&                                                & {\it run time (s)} &     9     &     36    &     54    &     192   &     427   &    2118   &  {\bf 2.80}\\%

		\multirow{6}{*}{$1.5$}&\specialcell{$Relaxed$\\$MIP solver$}& $f$     &{\it 15.83}&{\it 10.08}&{\it 15.14}&{\it 16.87}&{\it }&{\it }&  \specialcell{{\bf 1.00}\\-} \\%11495  
		&                                                & {\it run time (s)} &    10     &     43    &     72    &     262   &     58    &     352   &  1.00 \\% 439					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &   11.55   &   7.61   &   12.28   &   15.00   &   17.55   &   17.57   &  0.96  \\%  11012
		&                                                & {\it run time (s)} &    25     &    107   &     156   &    498    &    1217   &   5743     &  1.00 \\% 260

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &   17.05  &   10.01   &   15.01  &   16.75   &   20.09   &      &  0.87 \\% 9966
		&                                                & {\it run time (s)} &    18    &    64     &     101  &    351    &   828     &  120      &  {\bf 1.70}\\% 151

		\midrule
		\multirow{6}{*}{$2.0$}&\specialcell{$Relaxed$\\$MIP solver$}& $f$            &{\it }&{\it }&{\it }&{\it }&{\it }&{\it  }&  \specialcell{{\bf 1.00}\\-} \\%15266  
		&                                                & {\it run time (s)} &     < 1   &     3     &     5     &     20    &     58    &     352   &  1.00 \\% 439					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &      &      &      &       &       &       &   0.96  \\%  14666
		&                                                & {\it run time (s)} &     < 1   &     2     &     4     &     14     &     35     &   220     &  1.00 \\% 260

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &      &      &      &       &       &          &  0.94  \\% 14374
		&                                                & {\it run time (s)} &     < 1   &     2     &     3     &     9      &   26       &  151      &  {\bf 1.70}\\% 151

	\end{tabular}
}
	%\textsuperscript{asdf sd .}	
	\normalsize
\end{table}

@@

We solved all scenarios and instances with a MIP solver in a relaxed linear model. This is good for the reader to have an idea of the real performance differences between serial and parallel {\it Shims}.

{\it Shims} had a quality performance very close to the {\it Relaxed MIP solver} upper bound solution, and, as to the {\bf Speedup}, on average, {\it mpShims} was 2 times faster than {\it Shims}. Theoretically, it could be more, but due to the burden of sharing, for reading and writing, the CG deviation and the list of items among the processes (pallets), the {\it race condition} management limited {\it mpShims} performance.

@@

\vspace{2.0mm}
\begin{table}[!ht]
\centering
\caption{Parallel 3D packing time increment}  \label{tab:3d}
\scriptsize
\begin{tabular}{c S[table-format=-1.1] S[table-format=-1.1] S[table-format=-1.1]}
\toprule
&   \multicolumn{3}{c}{\bf Average tour time - 3D packing}  \\
\cmidrule{2-4}
& {\bf without} & {\bf with} & {\bf increment} \\
{\bf Scenario} & {\bf (s)}    & {\bf (s)}   & {\bf (times)} \\		
\midrule
$1$ &   1 &   15 & 15 \\ % 1	 9   , 3	 6, 1	 25	
$2$ &   5 &   76 & 15 \\ % 2	 36  , 13	 25
$3$ &   8 &   97 & 12 \\ % 3	 54  , 20	 41	
$4$ &  35 &  330 &  9 \\ % 12	 192 , 78	 158
$5$ &  98 &  740 &  8 \\ % 34	 427 , 198	 401
$6$ & 591 & 3709 &  6 \\ % 202	 2118, 1103	 2161                                                       
\bottomrule
\end{tabular}
\end{table}

@@

\vspace{2.0mm}
\begin{table}[!ht]
\centering
\caption{Average distances minimization}  \label{tab:ground}
%\footnotesize
\scriptsize
\begin{tabular}{c S[table-format=-1.1] S[table-format=-1.1] S[table-format=-1.3]}
\toprule
& {\bf Before} & {\bf After} & {\bf Improvement} \\
{\bf Scenario} & {\bf (m)}    & {\bf (m)}   & {\bf (\%)} \\		
\midrule
$1$ &  32.7 & 28.7 & -12.3 \\ % CBC 32.1 & 31.3 & -2.4 Shims 34.0 & 29.5 & -13.1, 31.5 & 29.9 & -5.1
$2$ & 193.3 & 188.9 & -2.3 \\ % mpShims 212.0 & 188.9 & -10.9
$3$ & 165.1 & 153.3 & -7.1 \\ % 
$4$ & 134.0 & 130.7 & -2.4 \\ % CBC 137.1 & 132.0 & -3.7 mpShim 143.4 & 136.6 & -4.7
$5$ & 118.0 & 116.1 & -1.6 \\ % CBC 124.9 & 116.3 & -6.9 mpShim 126.7 & 122.0 & -3.8 
$6$ & 105.2 & 104.8 & -0.4 \\ % CBC 117.4 & 107.6 & -8.3 mpShim 115.3 & 110.4 & -4.2                                                                
\bottomrule
\end{tabular}
\end{table}
